Geometrization of characters of tori over non-Archimedean local fields

### 2013-07-23 shanghai.tex
Working on diagrams for base change

\begin{proposition}
The following diagram commutes:
\[
\begin{tikzcd}
\CSiso{G} \rar{\nu} \dar{t_G} & \CSiso{G_{k'}} \dar{t_{G_{k'}}} \\
\Hom(G(k), \EEx) \rar{\Nm} & \Hom(G(k'), \EEx).
\end{tikzcd}
\]
\end{proposition}

We define a functor $\CS(G_{k'}) \to \CS(G)$ by.... \David{We can't define this by pullback
since $G_{k'} \to G$ goes in the wrong direction}
\begin{proposition} \label{prop:csbe}
The diagram
\[
\begin{tikzcd}
\CSiso{G_{k'}} \arrow[two heads]{r} \dar & \CSiso{G} \dar \\
\Hom(G(k'), \EEx) \arrow[two heads]{r} & \Hom(G(k), \EEx)
\end{tikzcd}
\]
commutes, where the vertical arrows are as in Theorem \ref{thm:snake}.
\end{proposition}

@@

\begin{proposition}
  Then the following diagram commutes:
\[
\begin{tikzcd}
\CSiso{G} \rar{t_G} \dar & \Hom(G(k'), \EEx) \dar \\
\CSiso{\Res_{k'/k} G} \rar{t_{\Res_{k'/k} G}} & \Hom((\Res_{k'/k}G)(k), \EEx)
\end{tikzcd}
\]
\end{proposition}

>>>>

\begin{proposition}
The following diagram commutes, where the bottom map is induced by the norm $G(k') \rightarrow G(k)$:
\[
\begin{tikzcd}
\CSiso{G} \rar{\nu} \dar{t_G} & \CSiso{G_{k'}} \dar{t_{G_{k'}}} \\
\Hom(G(k), \EEx) \rar{\Nm} & \Hom(G(k'), \EEx).
\end{tikzcd}
\]
\end{proposition}

In the opposite direction, there is a canonical closed immersion of $k$-schemes
$G \hookrightarrow \Res_{k'/k}(G_{k'})$ \cite[\S 7.6]{BLR}.  Pullback yields a functor
\[
\CS(\Res_{k'/k}(G_{k'})) \xrightarrow{\iota} \CS(G).
\]
\begin{proposition} \label{prop:csbe}
The following diagram commutes, where the bottom map is induced by the inclusion $G(k) \hookrightarrow G(k')$:
\[
\begin{tikzcd}
\CSiso{\Res_{k'/k}(G_{k'})} \arrow[two heads]{r}{\iota} \dar{t_{\Res_{k'/k}(G_{k'})}} & \CSiso{G} \dar{t_G} \\
\Hom(G(k'), \EEx) \arrow[two heads]{r} & \Hom(G(k), \EEx).
\end{tikzcd}
\]
\end{proposition}

@@

\begin{proposition}
  Then the following diagram commutes:
\[
\begin{tikzcd}
\CSiso{G'} \dar{t_{G'}} \rar & \CSiso{\Res_{k'/k} G'} \dar{t_{\Res_{k'/k} G'}} \\
 \Hom(G'(k'), \EEx) \rar & \Hom((\Res_{k'/k}G')(k), \EEx)
\end{tikzcd}
\]
\end{proposition}
